%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[line, margin]{res}
\usepackage{url}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}
\begin{document}
%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------
\name{Sajal Agrawal}
\address{\href{mailto: sajal.agrawal1997@gmail.com}{sajal.agrawal1997@gmail.com}\\ +918878155869}
\begin{resume}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{EDUCATION}
\textbf{B.E. in Computer Science and Engineering} \hfill 2019(Expected)\\
Shri G. S. Institute Of Technology And Science, Indore\\
CGPA: 7.8/10\\
\textbf{High School}- St. Norbert School, Indore (CBSE)- 96.6\%\hfill 2015\\
\textbf{Secondary School}- St. Norbert School, Indore (CBSE)- CGPA: 9.8/10\hfill 2013\\

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{TECHNICAL SKILLS}
Languages: C, C++, Java(basic)\\
Web Technology: HTML, CSS\\
Others: MySQL, \LaTeX\\

%----------------------------------------------------------------------------------------
%	ACHIEVEMENTS SECTION
%----------------------------------------------------------------------------------------
\section{ACHIEVEMENTS}
\begin{itemize}
\item Secured \textbf{AIR 4299} in IIT-JEE Mains 2015
\item Felicitated with Certificate of Merit by All India Senior School Certificate Examination (AISSCE) 2015 for being among the \textbf{top 0.1\% of successful candidates in Mathematics}.
\item Felicitated at St. Norbert Senior Secondary School, Indore for academic performance in 12th standard (C. B. S. E.) and for being \textbf{Indore City PCM Stream Topper (96.6\%)}.
\item Active participation on online competitive coding websites - \href{https://www.codechef.com/users/sajalagrawal}{CodeChef}, \href{https://www.hackerrank.com/sajalagrawal}{HackerRank}, \href{https://www.hackerearth.com/@sajal1}{HackerEarth}, \href{http://www.practice.geeksforgeeks.org/user-profile.php?user=sajalagrawal}{Geeksforgeeks} etc.
Member Handle - sajalagrawal(sajal1 on HackerEarth)
\item Won Gold Medal for securing \textbf{School Rank 1 in 16th SOF National Science Olympiad} in Class 11th, 2014.
\item Won Silver Medal and secured ‘A’ grade in Arithmetic Aptitude Test conducted by UCMAS Mental Arithmetic (India) Pvt. Ltd. in 2009.
\end{itemize}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------
\section{PROJECTS}
All of my project code is available on: \href{https://github.com/sajalagrawal}{https://github.com/sajalagrawal}
\begin{itemize}
\item\textbf{\href{https://github.com/sajalagrawal/Breakout-Game}{BreakOut Game}}:\hfill May 2016\\ A JAVA based Breakout game influenced by the game built by Steve Wozniak aided by Steve Jobs. The player has to eliminate all the layers of bricks present by hitting them with a ball bouncing off a paddle. It was a part of the Stanford's CS106A course.
\item\textbf{\href{https://github.com/sajalagrawal/Hangman-Game}{Hangman Game}}:\hfill June 2016\\ A JAVA based simple hangman game. The player has to correctly guess the hidden word by guessing the individual characters of the word. It was a part of the Stanford's CS106A course.
\end{itemize}

%----------------------------------------------------------------------------------------
%	ACTIVITIES SECTION
%----------------------------------------------------------------------------------------
\section{ACTIVITIES}
\begin{itemize}
\item Problem Setter \& Tester for the college coding competitions \href{https://www.hackerrank.com/contests/code-blitz-001/challenges}{Code-Blitz-001}, \href{https://www.hackerrank.com/contests/code-blitz-002/challenges}{Code-Blitz-002}, \href{https://www.codechef.com/MXPY2017}{Max Pay-in}.
\item Active member of 'CodeFosters Club' \& 'SGSITS Robotics Club'.
\end{itemize}

%----------------------------------------------------------------------------------------
%	HOBBIES SECTION
%----------------------------------------------------------------------------------------
\section{HOBBIES}
Competitive Coding, Watching movies

\end{resume}
\end{document}